### 2015-05-20 Paper_Markdown.Rmd
Explicitly load the RData files into memory.  These ought to be rds files at some point, but there's too much intertia right now.
Other minor reformatting.

```{r Fig4SampleLoss, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=6}

@@

loss <- ggplot(data = na.samples, aes(x=distance, y=size)) + 
  geom_path(aes(group=site, color = bin)) +
  scale_color_brewer(palette = 'PiYG', type = 'div') +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif'),
        axis.text = element_text(size=14, family='serif'),
        legend.position = 'none') +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  geom_segment(aes(x=0.48, 
                   xend = 0.48, 
                   y = min(mat.res$sample_size, na.rm=TRUE), 
                   yend = nrow(climate)), 
               size=1, color='red', linetype=2)

@@

loss.map <-  ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_polygon(aes(group=group), color='blue', alpha=0.2) +
  geom_point(data = loc.loss, 
             aes(x = long, y = lat, color = bin), alpha=0.7, size = 3) +
  theme_bw() +
  xlab('Longitude') + ylab('Latitude') +
  theme(axis.text=element_text(size=12, family='serif'),
        panel.background = element_rect(fill = 'lightblue'),
        legend.position = 'none') +
  coord_map(projection='albers', lat0=35, lat1=55, xlim=c(-100, -60), ylim=c(35, 80)) +
  scale_color_brewer(palette = 'PiYG', type = 'div')
  #scale_color_continuous(low = '#F08080', high='#4169E1')

>>>>

```{r Fig4SampleLoss, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=6}
load('data/mat.res.RData')
load('data/wa.res.RData')
load('data/wapls.res.RData')
load('data/brt.res.RData')
load('data/rfor.res.RData')

@@

loss <- ggplot(data = na.samples, aes(x=distance, y=size)) + 
  geom_path(aes(group=site, color = bin), alpha = 0.4) +
  scale_color_brewer(palette = 'PiYG', type = 'div') +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif'),
        axis.text = element_text(size=14, family='serif'),
        legend.position = 'none') +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  geom_segment(aes(x=0.48, 
                   xend = 0.48, 
                   y = min(mat.res$sample_size, na.rm=TRUE), 
                   yend = nrow(climate)), 
               size=1, color='red', linetype=2)

@@

loss.map <-  ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_polygon(aes(group=group), color='blue', alpha=0.2) +
  geom_point(data = loc.loss, 
             aes(x = long, y = lat, color = bin), alpha=0.4, size = 3) +
  theme_bw() +
  xlab('Longitude') + ylab('Latitude') +
  theme(axis.text=element_text(size=12, family='serif'),
        panel.background = element_rect(fill = 'lightblue'),
        legend.position = 'none') +
  coord_map(projection='albers', lat0=35, lat1=55, xlim=c(-100, -60), ylim=c(35, 80)) +
  scale_color_brewer(palette = 'PiYG', type = 'div')
  #scale_color_continuous(low = '#F08080', high='#4169E1')
